Bird species composition in coastal urban habitats

### 2020-11-16 Ms_HabitatAves.Rmd
eleccion de 6 sitios para grafico de ocupancia

Sitios <- read.csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% 
  dplyr::filter(Sitio %in% c("PLAZA ANIBAL PINTO", "PLAYA LA BOCA", "PLAZA GABRIELA MISTRAL", "LAGUNA VERDE")) %>% 
  mutate(Sitio= str_replace(Sitio, "PLAZA ANIBAL PINTO", "PAP"),
         Sitio= str_replace(Sitio, "PLAYA LA BOCA", "PLB"),
         Sitio= str_replace(Sitio, "PLAZA GABRIELA MISTRAL", "PGM"),
         Sitio= str_replace(Sitio, "LAGUNA VERDE", "LG")) %>% 
  dplyr::select(Sitio, Latitud, Longitud) %>% distinct() %>% st_as_sf(coords=c("Longitud","Latitud"),crs="+proj=longlat +datum=WGS84 +no_defs") %>% 
  st_transform(crs="+proj=utm +zone=19 +south +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")

ggplot() + geom_raster(data = Species_DF, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, 
nudge_x=-5000, nudge_y = 1000)+ 
  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=2)

@@

Sitios <- read.csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% 
  dplyr::filter(Sitio %in% c("PLAZA ANIBAL PINTO", "PLAYA LA BOCA", "PLAZA GABRIELA MISTRAL", "LAGUNA VERDE")) %>% 
  mutate(Sitio= str_replace(Sitio, "PLAZA ANIBAL PINTO", "PAP"),
         Sitio= str_replace(Sitio, "PLAYA LA BOCA", "PLB"),
         Sitio= str_replace(Sitio, "PLAZA GABRIELA MISTRAL", "PGM"),
         Sitio= str_replace(Sitio, "LAGUNA VERDE", "LG")) %>% 
  dplyr::select(Sitio, Latitud, Longitud) %>% distinct() %>% st_as_sf(coords=c("Longitud","Latitud"),crs="+proj=longlat +datum=WGS84 +no_defs") %>% 
  st_transform(crs="+proj=utm +zone=19 +south +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")

ggplot() + geom_raster(data = Species_DF, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, 
nudge_x=-5000, nudge_y = 1000)+ 
  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=2)

>>>>

Sitios <- read.csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% 
  dplyr::filter(Sitio %in% c("TERMINAL", "PLAYA LA BOCA", "PARQUE EL LITRE", "CALETA EL MEMBRILLO", "ROCA OCEANICA","SECTOR 5")) %>% 
  mutate(Sitio= str_replace(Sitio, "TERMINAL", "T"),
         Sitio= str_replace(Sitio, "PLAYA LA BOCA", "PLB"),
         Sitio= str_replace(Sitio, "PARQUE EL LITRE", "PEL"),
         Sitio= str_replace(Sitio, "CALETA EL MEMBRILLO", "CEM"),
         Sitio= str_replace(Sitio, "ROCA OCEANICA", "RO"),
         Sitio= str_replace(Sitio, "SECTOR 5", "PR")) %>% 
  dplyr::select(Sitio, Latitud, Longitud) %>% distinct() %>% st_as_sf(coords=c("Longitud","Latitud"),crs="+proj=longlat +datum=WGS84 +no_defs") %>% 
  st_transform(crs="+proj=utm +zone=19 +south +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")

OcuI <- ggplot() + geom_raster(data = Species_DF, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, 
nudge_x=-5000, nudge_y = 1000)+ 
  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=2)+ theme(legend.position = "bottom")

@@

Sitios <- read.csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% 
 dplyr::filter(Sitio %in% c("TERMINAL", "PLAYA LA BOCA", "PARQUE EL LITRE", "CALETA EL MEMBRILLO", "ROCA OCEANICA","SECTOR 5")) %>% 
  mutate(Sitio= str_replace(Sitio, "TERMINAL", "T"),
         Sitio= str_replace(Sitio, "PLAYA LA BOCA", "PLB"),
         Sitio= str_replace(Sitio, "PARQUE EL LITRE", "PEL"),
         Sitio= str_replace(Sitio, "CALETA EL MEMBRILLO", "CEM"),
         Sitio= str_replace(Sitio, "ROCA OCEANICA", "RO"),
         Sitio= str_replace(Sitio, "SECTOR 5", "PR")) %>% 
  dplyr::select(Sitio, Latitud, Longitud) %>% distinct() %>% st_as_sf(coords=c("Longitud","Latitud"),crs="+proj=longlat +datum=WGS84 +no_defs") %>% 
  st_transform(crs="+proj=utm +zone=19 +south +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")

OcuP <- ggplot() + geom_raster(data = Species_DF, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, 
nudge_x=-5000, nudge_y = 1000)+   theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + 
  labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=2)+ theme(legend.position = "bottom")

```{r, fig.height=10}

layout <- "
AAAABBB
AAAABBB
"
OcuI + OcuP+plot_layout(design = layout, guides = 'collect') +plot_annotation(tag_levels = 'A')
